Comparing tool variability and numerical variability in fMRI analyses

### 2021-08-23 paper/paper.tex
Add result figures in paper

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
\renewcommand{\baselinestretch}{1.1} 
%
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{ulem}
% \usepackage{geometry}
% \usepackage{marginnote}

@@

  \item[$\bullet$ Comparison metrics] comparing variabilities statistically by computing correlations between T-statistic values, Dice coefficient, 
                  and the number of significant digits.

@@

\begin{description}
  \item[$\bullet$ Figure 1: Showing results visually] make an overlay of 3 samples of un/thresholded activations maps for each condition.

  \item[$\bullet$ Table 1: Summary of statistics] mean differences and correlations between T-statistic values for each pair of results in each condition.

  \item[$\bullet$ Figure 2: Bland-Altman] comparing unthresholded group level maps, 2D histogram, computed each pair of tools in both conditions.
                  Measures similarity between statistic values.
                  This plots difference between the statistic values (y-axis) and the mean statistic value (x-axis) for all voxels.

  \item[$\bullet$ Figure 3: Dice Coefficient] comparing the thresholded group level maps computed each pair of tools in both conditions.
                  Measures the overlap of voxels which assess the spatial similarity between activated maps.

  \item[$\bullet$ Figure 4: Significant digits] comparing the distribution of SD across 3 samples (unthresholded images) for each condition. 
                  Find and show results at the precision that creates the most similar numerical uncertainty with between tool variability.  
\end{description}

% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
% are responsible for disparities between pair of images.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
\renewcommand{\baselinestretch}{1.1} 
%
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{ulem}

\usepackage[para,online,flushleft]{threeparttable}
\usepackage{booktabs}
\usepackage{multirow}
% \usepackage{geometry}
% \usepackage{marginnote}

@@

  \item[$\bullet$ Comparison metrics] comparing variabilities statistically by computing correlations between T-statistic values, Dice coefficient, 
                  and the number of significant digits.    
% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
% are responsible for disparities between pair of images.

@@

% \subsection{Comparing between tool and numerical variability}
\begin{description}
  \item[$\bullet$ Table 1: Summary of statistics] mean and standard deviation of the differences, and correlations 
                  between t-statistic values for each pair of results in each condition.

  \item[$\bullet$ Figure 1 and 2: Surface maps of std.] comparing standard deviations on surface map template (ICBM-152)
                  computed between pair of software (tool variation), and different Fuzzy samples on each software (numerical variation).
                  Figure 1 shows results for group level thresholded t-statistics, and 
                  Figure 2 shows maps for group level unthresholded t values. The numerical variation

  \item[$\bullet$ Figure 3 and 4: Dice Coefficients] comparing region-by-region Dice coefficients of group level thresholded maps between tools.
                  This measures the overlap of voxels which assess the spatial similarity between activated maps.
                  In bewteen tool similarity, the Dice values correspond to the mean of Dices computed for each pair of that specific tool,
                  for example, Dice value for SPM is calculated by averaging Dices in SPM-AFNI and SPM-FSL pairs.
                  Similarly, Dice values are computed between three Fuzzy samples obtained from each tool in numerical variation.
                  Figure 3 shows bar plots of Dices for negative and positive activated regions.
                  Figure 4 shows surface maps of Dices for the activated regions.

  % \item[$\bullet$ Figure 2: Bland-Altman] comparing unthresholded group level maps, 2D histogram, computed each pair of tools in both conditions.
  % Measures similarity between statistic values.
  % This plots difference between the statistic values (y-axis) and the mean statistic value (x-axis) for all voxels.

  % \item[$\bullet$ Figure 4: Significant digits] comparing the distribution of SD across 3 samples (unthresholded images) for each condition. 
  %                 Find and show results at the precision that creates the most similar numerical uncertainty with between tool variability.

%%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{10pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccc|ccc}
        \toprule
        \multirow{2}{*}{} & \multicolumn{3}{c}{Thresholded} & \multicolumn{3}{c}{Unthresholded} \\
        \cmidrule{2-4} \cmidrule{5-7} \\
        {} & Mean diff. & Std. diff. & Corr. & Mean diff. & Std. diff. & Corr.  \\
        \midrule
        \rowcolor{lightgray}
        FSL vs. SPM          &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
        \rowcolor{lightgray}
        FSL vs. AFNI         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
        \rowcolor{lightgray}
        AFNI vs. SPM         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
        Fuzzy SPM            &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
        Fuzzy FSL            &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
        Fuzzy AFNI           &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of t-statistics mean and standard deviation of differences and correlations of each pair of tools.}
    \label{table:pipeline-stats}
\end{table}

%%%%%%%%%% STD. of Thresh %%%%%%%%
\begin{figure}[b]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  \begin{subfigure}[t]{\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh(std).pdf}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \label{fig:thresh-stdmaps1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/maps-on-surf-mca-thresh(std).pdf}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \label{fig:thresh-stdmaps2}
  \end{subfigure}
  \caption{Surface maps of standard deviation of thresholded t-statistics.}
  \label{fig:thresh-stdmaps}
  \end{minipage}}
\end{figure}

%%%%%%%%%% STD. of Unthresh %%%%%%%%
\begin{figure}[b]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  \begin{subfigure}[t]{\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-tool(std).pdf}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \label{fig:thresh-stdmaps1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-mca1(std).pdf}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \label{fig:thresh-stdmaps2}
  \end{subfigure}
  \caption{Surface maps of standard deviation of unthresholded t-statistics.}
  \label{fig:thresh-stdmaps}
  \end{minipage}}
\end{figure}

%%%%%%%%%% Bar plots of Dices from Thresh %%%%%%%%
\begin{figure}[b]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}

      \begin{subfigure}[t]{0.5\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figures/spm-exc_set_file.png}
        \label{fig:fsl-dices}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.5\linewidth}
        \centering
        \includegraphics[width=\linewidth]{figures/spm-exc_set_file_neg.png}
        \label{fig:spm-dices}
      \end{subfigure}    
  \hfill
    \begin{subfigure}[t]{0.5\linewidth}
      \centering
      \includegraphics[width=\linewidth]{figures/fsl-exc_set_file.png}
      \label{fig:fsl-dices}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.5\linewidth}
      \centering
      \includegraphics[width=\linewidth]{figures/fsl-exc_set_file_neg.png}
      \label{fig:spm-dices}
    \end{subfigure}  
  \hfill
    \begin{subfigure}[t]{0.5\linewidth}
      \centering
      \includegraphics[width=\linewidth]{figures/afni-exc_set_file.png}
      \label{fig:fsl-dices}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.5\linewidth}
      \centering
      \includegraphics[width=\linewidth]{figures/afni-exc_set_file_neg.png}
      \label{fig:spm-dices}
    \end{subfigure}

  \caption{Bar plots of Dice coefficients of activated regions between pair of tools (BT) and fuzzy samples (FL) from the thresholded t-statistics.
  Right plots show the negative maps, and left plots show the positive maps. 
  Region numbers correspond to the 180 areas of cortical parcellation (HCP-MMP1.0)~\cite{Glasser-nature}.}
  \label{fig:unthresh-dices}
  \end{minipage}}
\end{figure}

%%%%%%%%%% Surf maps of Dices from Thresh %%%%%%%%
\begin{figure}[b]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  \begin{subfigure}[t]{\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/maps-on-surf-SPM(dice).pdf}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \label{fig:thresh-stdmaps1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/maps-on-surf-FSL(dice).pdf}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \label{fig:thresh-stdmaps1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/maps-on-surf-AFNI(dice).pdf}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \label{fig:thresh-stdmaps2}
  \end{subfigure}
  \caption{Surface maps of Dice coefficients of thresholded t-statistics region-by-region.}
  \label{fig:unthresh-dices}
  \end{minipage}}
\end{figure}

% \subsection{The precision that Fuzzy FSL tool can simulate the between tool variations}
% \begin{description}
%   \item[$\bullet$ Figure 5:] Repeat Fig 1-4 for the results of Fuzzy FSL on the precision that simulate mostly betwen tool varions.
% \end{description}
